Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-08-15 ms.tex
Tom updated the table of sensitivities with tradeoffs.

\begin{table}[!hb]
\centering
\begin{tabular}{llll}
\hline \hline
Sub-Array Size &  LW Saturation & \# of DHS & DHS Noise\\
               &  K Magnitude   &           & ppm \\
\hline \hline
2048$\times$ 64 & 4.52 & 1 &  ?? \\
2048$\times$ 128 & 5.26 & 1 &  ?? \\
2048$\times$ 256 & 6.01 & 2 &  ?? \\
2048$\times$ 2048 & 8.26 & 10 & ?? \\
\hline
\end{tabular}
\caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes.
The size affects the number of DHS that can be included, so the SNR at 1.5$\mu$m in the DHS spectrum at the given saturation limit for a 1 hour transit is shown in column 4.}\label{tab:SatSNRsubA}
\end{table}

>>>>

\begin{table}[!hb]
\centering
\begin{tabular}{llrr}
\hline \hline
Sub-Array Size &  LW Saturation & \# of DHS & DHS Noise\\
               &  K Magnitude   &           & ppm \\
\hline \hline
2048$\times$ 64 & 4.52 & 1 &  72 -- 110 \\
2048$\times$ 128 & 5.26 & 1 &  100 -- 160 \\
2048$\times$ 256 & 6.01 & 2 &  100 -- 160 \\
2048$\times$ 2048 & 8.26 & 10 & 160 -- 270 \\
\hline
\end{tabular}
\caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes.
The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4.}\label{tab:SatSNRsubA}
\end{table}
